%-------------------------
% Resume in LaTeX
% Based on template by Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://elowenluo.com/}{\Large Elowen Luo}} & Email: \href{mailto:elowen.luo@gmail.com}{elowen.luo@gmail.com}\\
  \href{https://github.com/elowenluo/}{github.com/ElowenLuo} & Location: Chongqing, China \\
\end{tabular*}

%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
  \resumeItemListStart
    \resumeItem{Profile}{Full-stack developer and lifelong learner with a forward-thinking approach to engineering. Skilled at transforming complex data into intuitive visual interfaces. Passionate about code quality, development efficiency, and continuously exploring new technologies to solve practical problems.}
  \resumeItemListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Front-end Development Engineer}{Chongqing, China}
      {\href{http://www.cisdiinfo.com/}{Chongqing Dinghui Information Technology Co., Ltd. (CISDI Info)}}{Jul 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Factory Data Visualization Platform}
          {Developed interactive visualization dashboards using Vue3 and TypeScript. Implemented complex data visualizations with Echarts and optimized performance for rendering large datasets.}
        \resumeItem{Responsive Mobile Interface}
          {Designed and implemented responsive UI for mobile devices, significantly improving user experience across different screen sizes.}
        \resumeItem{Component Library}
          {Built a reusable front-end component library that streamlined development and reduced code duplication across multiple projects.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Article Processor}{Personal Project}
      {Full-stack Developer}{Jan 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Overview}
          {Content processing tool built with Node.js and Express that supports batch article formatting and AI content enhancement, reducing news processing time by 50\%.}
        \resumeItem{Technology}
          {Node.js, Express, OpenAI API, Google AI API, JavaScript, REST API design}
        \resumeItem{Project URL}
          {\href{https://articlesprocessor.elowenluo.com/}{articlesprocessor.elowenluo.com}}
      \resumeItemListEnd
      
    \resumeSubheading
      {Autofill WordPress}{Browser Extension}
      {Front-end Developer}{Feb 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Overview}
          {Tampermonkey browser extension that automatically fills WordPress article forms and integrates with Article Processor for batch content management.}
        \resumeItem{Technology}
          {JavaScript, DOM manipulation, Tampermonkey API, REST API integration}
        \resumeItem{Project URL}
          {\href{https://github.com/elowenluo/browser-scripts/blob/main/tampermonkey/autofill-wordpress/README.md}{github.com/elowenluo/browser-scripts}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chongqing Elite Institute of Engineering}{Chongqing, China}
      {Intelligent Vehicle Software; GPA: 3.9/4.0}{Sep 2022 -- May 2023}
      \resumeItemListStart
        \resumeItem{Coursework}
          {Intelligent Connected Vehicle Systems, Automotive Software Development Fundamentals, Vehicle Network Systems and Applications, Intelligent Driving Algorithm Foundations}
      \resumeItemListEnd
    \resumeSubheading
      {Chongqing University of Posts and Telecommunications}{Chongqing, China}
      {B.Eng. in Data Science and Big Data Technology; GPA: 3.1/4.0}{Sep 2019 -- Jun 2023}
      \resumeItemListStart
        \resumeItem{Coursework}
          {Computer Networks, Algorithm Analysis and Design, Database Principles, Operating Systems}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: HTML, CSS, JavaScript, TypeScript, Rust}
    }
    \item{
      \textbf{Frameworks}{: Vue 2/3, Vue Router, Vuex, Tokio, Axum}
    }
    \item{
      \textbf{CSS}{: Sass, Less}
    }
    \item{
      \textbf{Visualization}{: Echarts}
    }
    \item{
      \textbf{Tool Development}{: Node.js, Express}
    }
    \item{
      \textbf{Version Control}{: Git, GitHub}
    }
    \item{
      \textbf{Languages}{: Chinese (Native), English (CET-4)}
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}